Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-02-03 GECCO/volunteer-clouds-gecco16.tex
Try to use 'secondly'... though this was an American paper OK. Anyway, try to avoid 'second' if you do not have a 'first'

Nowadays there is a big and increasing number of distributed
evolutionary computation (EC) software frameworks available, usually
as open source frameworks \cite{Parejo12Survey}.  Most of them have
two features: they are {\em desktop} applications, that is, they must
be compiled or run directly on the operating system layer and, second,
they assume that the nodes that are going to run the system are under
the control of developers or they at least have access to them.

>>>>

Nowadays there is a big and increasing number of distributed
evolutionary computation (EC) software frameworks available, usually
as open source frameworks \cite{Parejo12Survey}.  Most of them have
two features: they are {\em desktop} applications, that is, they must
be compiled or run directly on the operating system layer and, in addition,
they assume that the nodes that are going to run the system are under
the control of developers or they at least have access to them.
